%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Conclusions.tex                                     %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Conclusions}
\label{chapter:conclusions}

\quad In conclusion, during this semester some progress was already made for the final objective of my thesis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\label{section:achievements}

\quad During this semester there were both teorical and pratical achievements. A pratical aplication achivement was the development of the IOb-SoC simulation with cocotb (based on python) and the rewriting of the console to python. A teorical achivement was understanding the hardware requirements in a CPU in order to be able to boot Linux.


% ----------------------------------------------------------------------
\section{Future Work}
\label{section:future}

\quad During the next semester it's when the rest and most of my thesis work will be developed. And during the thesis development a Linux distribution is to be compiled and booted on to the IOb-SoC with a RISC-V processor. The integration of a RISC-V processor is going to be completed on the next semester. There are two possibile solution, either a costum CPU is developed and implemented on the IOb-SoC or a already existing CPU is adapted in order to work with the other IOb-SoC components and implement in it. After that .... boot linux, find linux distribution, 
