%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     File: ExtendedAbstract_abstr.tex                               %
%     Tex Master: ExtendedAbstract.tex                               %
%                                                                    %
%     Author: Andre Calado Marta                                     %
%     Last modified : 2 Dez 2011                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The abstract of should have less than 500 words.
% The keywords should be typed here (three to five keywords).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Abstract
%%
\begin{abstract}

The objective of this work is to accelerate an object detection application
using the VersatCNN, a Coarse Grained Reconfigurable Array (CGRA) architecture
developed for efficient inference of Convolutional Neural Network (CNN). The
performance objective is to enable real-time execution - 30 frames per second -
on low-end embedded systems.
The object detection application accelerated is the Tiny YOLOv3, based on a CNN
developed for constrained environments. The Tiny YOLOv3 network is composed of
Convolutional, Maxpool, Route, Upsample and Yolo layers. The application also
includes pre and post-processing routines. 
This thesis work uses the IOb-SoC, a RISC-V based system on a chip (SoC) from
IObundle as a baseline hardware platform for the project development.
Peripheral modules for measuring performance and enabling ethernet communication
are integrated into the IOb-SoC. The embedded version of Tiny YOLOv3 is
profilled for RISC-V only execution to identify the parts that require
acceleration. The VersatCNN is integraded into the system as a peripheral. The
work mainly focuses on the design of CGRA dataflow configurations, as the
different parts of the application require distinct configuration strategies for
the multiple layer types and the pre and post-processing routines. 
The final system achieves over 30 FPS for the complete Tiny YOLOv3, with a clock
frequency of 143~MHz and a 832x parallelism factor for convolutional operations.
\newline
\\
%%
%% Keywords (max 5)
%%
\noindent{{\bf Keywords:}} Object Detection, Convolutional Neural Networks,
Systems on Chip, Coarse Grained Reconfigurable Arrays. \\

\end{abstract}

